Chatbots and messaging platforms in the classroom: an analysis from the teacher's perspective

### 2021-11-05 edubots_surveys.Rnw
Rephrasing of the attitudes
Rephrased the last paragraph in the state of the art section to avoid the multiple use of opinions and clarify the use of attitudes in the TAM study.

On the other hand, teaching-oriented chatbots are more sophisticated,
as they set personalised learning outcomes and monitor learning
progress. For instance, \cite{fernoagua2018intelligent} reported on
``eduAssistant'', a virtual teaching assistant chatbot developed on the
Telegram messaging platform. In this study, Telegram platform was
chosen because it is easy to use, students are familiar with its
features, and it enables them to exchange messages in different
formats (text, audio and video) \cite{fernoagua2018intelligent}. In
addition, Telegram could operate on all devices and operating
systems. The ``eduAssistant'' chatbot acts as an automatic agent
in teacher-content-student, facilitating real-time feedback
loops and providing a personalised learning experience relevant to the
students' acquired skills and knowledge. Using this chatbot, educators can
create interactive instances in their lectures where they pose
questions to their students and the chatbot assists those who need
further help by giving them more hints and reporting it to their
educator's dashboard \cite{fernoagua2018intelligent}. This can help 
educators to locate those students that need their attention and send to 
them more educational resources relevant to their academic attainment.

@@

Regarding the factors for the adoption of chatbots in higher
education, many studies have focused on the evaluation of technology
acceptance and usability \cite{Roblyer2010,Pimmer2019}. However,
higher education is a special domain where, according to Hobert \cite{hobert2019you}, 
specific pedagogical factors such as learning success or increased motivation are more important.  
Therefore, to develop efficient chatbots for higher education, all stakeholders'
(i.e. educators, students, institutions, etc) needs should be
carefully collected and taken into consideration
\cite{sjostrom2018designing,tsivitanidouusers}.

Along this line of research, our previous work \cite{MoraChatbots2021:anon} aimed at analysing the expectations of students on this regard; recent papers have also analysed how the use of chatbots affected the learning outcomes of students in a Chinese class \cite{doi:10.1177/0735633120929622}. This paper analysed conversational chatbots in an one-to-one setting, finding that learning really benefited from it. This is, once again, a proof of the benefit of chatbots in certain settings; however, there are some opinions that might prevent the successful acceptance of the technology, and these are what we are trying to find out in this paper, together with what kind of features would make its acceptance better.

Besides, the present work is focused on the other key actor in this challenge, i.e. educators. Their attitudes have been studied very recently by Chocarro et al. \cite{doi:10.1080/03055698.2020.1850426}, who, by analysing surveys, created a {\em technology acceptance model} that proposed a series of features that would make chatbots easier to accept; among them, formality of language as well as easiness and usefulness. The survey targeted primary and secondary education teachers, and was also more interested in the general use of chatbots in education, not specifically in a classroom setting, seeking educational outcomes. However, they establish a series of results that are obviously interesting and relevant for this work.

We will present next the methodology we have followed to find out teachers' opinions.

>>>>

On the other hand, teaching-oriented chatbots are more sophisticated,
as they set personalised learning outcomes and monitor learning
progress. For instance, \cite{fernoagua2018intelligent} reported on
''eduAssistant'', a virtual teaching assistant chatbot developed on the
Telegram messaging platform. In this study, Telegram platform is
chosen because it is easy to use, students are familiar with its
features, and it enables them to exchange messages in different
formats (text, audio and video) \cite{fernoagua2018intelligent}. In
addition, Telegram could operate on all devices and operating
systems. The ''eduAssistant'' chatbot acts as an automatic agent
in teacher-content-student, facilitating real-time feedback
loops and providing a personalised learning experience relevant to the
students' acquired skills and knowledge. Using this chatbot, educators can
create interactive instances in their lectures where they pose
questions to their students and the chatbot assists those who need
further help by giving them more hints and reporting it to their
educator's dashboard \cite{fernoagua2018intelligent}. This can help 
educators locate those students that need more attention and send
them more educational resources relevant to their academic attainment.
In addition, a recent study has analysed how the use of chatbots positively affected the learning outcomes of students in a Chinese 
class \cite{doi:10.1177/0735633120929622}.

@@

Regarding the factors for the adoption of chatbots in higher
education, many studies have focused on the evaluation of technology
acceptance and usability \cite{Roblyer2010,Pimmer2019}. However,
higher education is a special domain where, according to Hobert \cite{hobert2019you}, 
specific pedagogical factors such as learning success and increased motivation are more important.  
Therefore, to develop efficient chatbots for higher education, all stakeholders'
(i.e. educators, students, institutions, etc) expectations needs to be
carefully collected and taken into consideration \cite{sjostrom2018designing,tsivitanidouusers}. 
As our previous work \cite{MoraChatbots2021:anon} aimed to present a detailed analysis of students' expectations and needs in this regard, the
present study focuses on investigating the needs of educators. In a recent study, Chocarro et al. \cite{doi:10.1080/03055698.2020.1850426} 
examined educators' acceptance of chatbots using TAM (Technology Acceptance Model) and proposed a series of features such as formality
 of language as well as usefulness to make chatbots easier to adopt.

In the next section, we will present the methodology adopted to collect teachers' responses.
